Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-13 paper/paper.tex
section title for k=3 case

\subsection{$O(\ell)$-competitive algorithm for $k=3$}

Let \emph{GREEDY} be the algorithm that on each inter-cluster request
 moves to arbitrary perfect partition \maciek{of input} closest (i.e. reachable in minimum number of node swaps) to the current one.

\begin{lemma} \label{lemma:k=3}
  Every re-balancing cost of GREEDY for $k=3$ is $O(1)$.
  %\maciek{GREEDY = find the cheapest (closest to the current) feasible partition}
  \maciek{We need to add to the assumption that the input has a perfect partition}
  \label{rebalancing-cost}
\end{lemma}

@@

\begin{theorem}
  Algorithm \emph{GREEDY} is $O(\ell)$-competitive when $k=3$.
  \maciek{Assumming the perfect partition of input sequence}
\end{theorem}

>>>>

%\subsection{$O(\ell)$-competitive algorithm for $k=3$}
\subsection{A Simpler Algorithm for $k=3$}
In this section,
we give an alternative algorithm for the special case of $k=3$.
The algorithm does not  improve upon PPL (asymptotically),
but we will use it in Section \ref{sec:generalModel} for the same special case in the general model.

Let \emph{GREEDY} be the algorithm that on each inter-cluster request
 moves to a perfect partition
% \maciek{of input}
closest to the current partition,
i.e.,
reachable in minimum number of node swaps (ties broken arbitrarily).

\begin{lemma} \label{lemma:k=3}
  Every re-balancing cost of GREEDY for $k=3$ is $O(1)$.
  %\maciek{GREEDY = find the cheapest (closest to the current) feasible partition}
  \maciek{We need to add to the assumption that the input has a perfect partition
  \mahmoud{the section now is only about PP model}}
  \label{rebalancing-cost}
\end{lemma}

@@

\begin{theorem}
  Algorithm \emph{GREEDY} is $O(\ell)$-competitive when $k=3$.
  \maciek{Assumming the perfect partition of input sequence
  \mahmoud{the section now is only about PP model}}
\end{theorem}
